---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {imdvizzer}

{imdvizzer} is designed to visualise England's [Index of Multiple Deprivation (IMD)](https://en.wikipedia.org/wiki/Multiple_deprivation_index) data in as many ways (or as few) as needed.  

The main data source is the [2019 IMD data from the Ministry of Housing, Communities & Local Government](https://www.gov.uk/government/statistics/english-indices-of-deprivation-2019).  This data was published with a [suite of additional mapping resources](https://www.gov.uk/guidance/english-indices-of-deprivation-2019-mapping-resources).  In particular this [zoomable map](https://dclgapps.communities.gov.uk/imd/iod_index.html) may be of interest.

For convenience and ease of extension {imdvizzer} uses the [{geographr}](https://github.com/humaniverse/geographr) package for map geometries and area lookup files, and the [{IMD}](https://github.com/humaniverse/IMD) package for IMD data.


## Usage

The first function implemented plots maps of IMD data for each English Integrated Care Board (ICB).  It can be used as follows:

```{r example, echo=TRUE, message=FALSE, warning=FALSE}
library(imdvizzer)

map_imd_icb("NHS Nottingham and Nottinghamshire Integrated Care Board")

```

## All English ICBs

This is the 2019 IMD data plotted for every ICB.  The individual regions plotted are [Lower Layer Super Output Areas (LSOAs)](https://en.wikipedia.org/wiki/GSS_coding_system#Neighbourhood_Statistics_Geography), which are consistent small geographical regions with populations of on average 1500 people.  Note that the x and y axis scales of these individual maps are not intended to be consistent.  The colour scales are consistent across the maps.

```{r all_icbs, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

icb_names <- geographr::lookup_lsoa11_sicbl22_icb22_ltla22 |>
  dplyr::arrange(icb22_name) |>
  dplyr::pull(icb22_name) |>
  unique()

data <- icb_names |>
    purrr::set_names() |>
    purrr::map(imdvizzer::map_imd_icb, include_title = FALSE)

for(i in 1:length(data)){
  
  cat("####", data[[i]][["name"]], "\n\n")
  
  plt <- data[[i]][["plot"]]
  print (plt)
  
  cat("\n\n", "---", "\n\n")
  
}

cat("END")

```
